Supplementary Figure 2c

### 2017-11-18 inst/figure2e_P1shRNAdox/figure2e_P1shRNAdox.Rmd
working on figures

pdf <- p + 
  geom_linerange(
    data = stats,
    aes(
      x = treatment, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment, 
      y = mean, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = treatment, 
      y = CI95h + 0.2,
      label = pFormat,
      group = plotGOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    position = position_dodge(width = 0.9),
    fill = "white",
    size = 1,
    family = "Arial Unicode MS"
  ) +
  guides(fill = guide_legend(
    title = "Gene",
    override.aes = list(size = 4)
  ))

>>>>

pdf <- p + 
  geom_linerange(
    data = stats,
    aes(
      x = treatment, 
      ymin = CI95l, 
      ymax = CI95h, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = treatment, 
      y = mean, 
      group = plotGOI
    ),
    colour = "gray20",
    position = position_dodge(width = 0.9),
    shape = 95,
    show.legend = FALSE
  ) +
  geom_label(
    data = stats,
    aes(
      x = treatment, 
      y = CI95h + 0.2,
      label = pFormat,
      group = plotGOI
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    position = position_dodge(width = 0.9),
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  ) +
  guides(fill = guide_legend(
    title = "Gene",
    override.aes = list(size = 4)
  ))

### 2017-11-18 inst/figure3a_stableLineExpression/figure3a_stableLineExpression.Rmd
working on figures

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = `Genetic mod`,
      ymin = CI95l,
      ymax = CI95h,
      group = interaction(`Genetic mod`, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = `Genetic mod`,
      y = mean,
      group = interaction(`Genetic mod`, GOI)
    ),
    colour = "gray20",
    shape = 95,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.4, 
      label = pFormat, 
      group = interaction(`Cell line`, GOI)
    ),
    fill = "white",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 1
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

>>>>

pdf <- p +
  geom_linerange(
    data = stats,
    aes(
      x = `Genetic mod`,
      ymin = CI95l,
      ymax = CI95h,
      group = interaction(`Genetic mod`, GOI)
    ),
    position = position_dodge(width = 0.9),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(
      x = `Genetic mod`,
      y = mean,
      group = interaction(`Genetic mod`, GOI)
    ),
    colour = "gray20",
    shape = 95,
    position = position_dodge(width = 0.9),
    show.legend = FALSE
  ) +
  geom_label(
    data = vl,
    aes(
      x = 1.5, 
      y = max + 0.4, 
      label = pFormat, 
      group = interaction(`Cell line`, GOI)
    ),
    fill = "white",
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    position = position_dodge(width = 0.9),
    show.legend = FALSE,
    fontface = "bold",
    family = "Arial Unicode MS",
    size = 1.5
  ) +
  geom_segment(
    data = vl,
    aes(
      x = x,
      y = max,
      xend = xend,
      yend = max
    ),
    colour = "grey43",
    size = 0.1,
    show.legend = FALSE
  ) +
  guides(
    fill = guide_legend(
      title = "Gene", 
      override.aes = list(size = 4)
    )
  )

### 2017-11-18 inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.Rmd
added gatherFigures and clearFigures functions and ran
working on figures

@@

markdown <- p +
    geom_linerange(
    data = stats,
    aes(x = condition, ymin = CI95l, ymax = CI95h),
    colour = "gray20",
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(x = condition, y = mean),
    colour = "gray20",
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  geom_segment(
    data = filter(stats, condition == "PC3 miR34a asRNA"),
    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
    colour = "grey43"
  ) +
  geom_label(
    data = stats,
    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  )

@@

pdf <- p +
    geom_linerange(
    data = stats,
    aes(x = condition, ymin = CI95l, ymax = CI95h),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(x = condition, y = mean),
    colour = "gray20",
    shape = 95,
    show.legend = FALSE
  ) +
  geom_segment(
    data = filter(stats, condition == "PC3 miR34a asRNA"),
    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
    colour = "grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  )

@@

# ggsave(
#   plot = figure, 
#   filename = path, 
#   device = cairo_pdf, 
#   height = 60,
#   width = 83,
#   units = "mm"
# )
```

>>>>

#prepare for plotting
data <- data %>%
  mutate(
    condition = gsub("PC3 miR34a asRNA", "PC3 miR34a\nasRNA", condition),
    condition = parse_factor(condition, levels = c("PC3 mock", "PC3 miR34a\nasRNA"))
  )

stats <- stats %>%
  mutate(
    condition = gsub("PC3 miR34a asRNA", "PC3 miR34a\nasRNA", condition),
    condition = parse_factor(condition, levels = c("PC3 mock", "PC3 miR34a\nasRNA"))
  )
```

@@

markdown <- p +
    geom_linerange(
    data = stats,
    aes(x = condition, ymin = CI95l, ymax = CI95h),
    colour = "gray20",
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(x = condition, y = mean),
    colour = "gray20",
    shape = 95,
    size = 6,
    show.legend = FALSE
  ) +
  geom_segment(
    data = filter(stats, condition == "PC3 miR34a\nasRNA"),
    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
    colour = "grey43"
  ) +
  geom_label(
    data = stats,
    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 5,
    family = "Arial Unicode MS"
  )

@@

pdf <- p +
    geom_linerange(
    data = stats,
    aes(x = condition, ymin = CI95l, ymax = CI95h),
    colour = "gray20",
    size = 0.1,
    show.legend = FALSE
  ) +
  geom_point(
    data = stats,
    aes(x = condition, y = mean),
    colour = "gray20",
    shape = 95,
    show.legend = FALSE
  ) +
  geom_segment(
    data = filter(stats, condition == "PC3 miR34a\nasRNA"),
    aes(x = 1, y = CI95h + 0.25, xend = 2, yend = CI95h + 0.25),
    colour = "grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(x = 1.5, y = CI95h + 0.45, label = pFormat),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  )

@@

ggsave(
  plot = figure,
  filename = path,
  device = cairo_pdf,
  height = 60,
  width = 43,
  units = "mm",
  dpi = 10000000
)
```

### 2017-11-18 inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.Rmd
working on figures

pdf <- p + 
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    shape = 95
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.4,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 2,
    family = "Arial Unicode MS"
  ) +
   geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20",
    size = 0.1
  )

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.pdf"
ggsave(
  plot = figure, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 83,
  units = "mm"
)
```

>>>>

pdf <- p + 
  geom_point(
    data = stats,
    aes(
      x = condition,
      y = mean
    ),
    colour="gray20",
    shape = 95
  ) +
  geom_segment(
    data = stats,
    aes(
      x = 1,
      y = max(CI95h) + 0.25,
      xend = 2,
      yend = max(CI95h) + 0.25
    ),
    colour="grey43",
    size = 0.1
  ) +
  geom_label(
    data = stats,
    aes(
      x = 1.5,
      y = max(CI95h) + 0.4,
      label = pFormat
    ),
    label.size = 0,
    label.padding = unit(0.01, "lines"),
    show.legend = FALSE,
    fill = "white",
    size = 1.5,
    family = "Arial Unicode MS"
  ) +
   geom_linerange(
    data = stats,
    aes(
      x = condition,
      ymin = CI95l,
      ymax = CI95h
    ),
    colour="gray20",
    size = 0.1
  )

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.pdf"
ggsave(
  plot = figure, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 43,
  units = "mm"
)
```
